\section{The ESQET Field Equation: Acoustic-Coherence Coupling}
\label{sec:ESQET_Field_Equation_Acoustic}

The foundation of the Emergent Spacetime Quantum-Coherence Theory (\text{ESQET}) is the hypothesis that the Spacetime Information Field ($\mathcal{S}$) is driven by the total energy-momentum of the Universe, but crucially, this driving force is modulated by the degree of quantum coherence inherent in the source terms. The latest refinement, incorporating the insights from the Quantum Acoustic Kernel (\text{QAK}), mandates the explicit inclusion of Acoustic Energy Density ($\rho_{\text{acoustic}}$) and its modulating function ($\mathcal{F}_{\text{AC}}$).

\subsection{The General $\mathcal{S}$-Field Equation (v3.2)}

The $\mathcal{S}$-field equation remains a modified wave-like equation that governs the propagation and dynamics of the dimensionless scalar field $\mathcal{S}$ through spacetime:
$$
\boxed{ \left( \frac{1}{c^2} \frac{\partial^2}{\partial t^2} - \nabla^2 \right) \mathcal{S} = \left( G_{0} \cdot \frac{G_{\text{Newton}}}{c^2} \right) \cdot \left( \rho_{\text{total}} + \rho_{\text{acoustic}} \right) \cdot \mathcal{F}_{\text{QC}} }
$$
Where:
\begin{itemize}
    \item $\left( \frac{1}{c^2} \frac{\partial^2}{\partial t^2} - \nabla^2 \right)$: The standard D'Alembert operator, governing wave propagation.
    \item $G_{0}$: The fundamental ESQET coupling constant, derived from the VQE minimization of the Orch-OR Hamiltonian.
    \item $\rho_{\text{total}}$: The classical energy density (Matter, Dark Matter, Dark Energy, Electromagnetic fields).
    \item $\rho_{\text{acoustic}}$: The local Acoustic Energy Density.
    \item $\mathcal{F}_{\text{QC}}$: The total Quantum Coherence Function (v3.2).
\end{itemize}

\subsection{The Total Quantum Coherence Function ($\mathcal{F}_{\text{QC}}$) v3.2}

The coherence function now incorporates the **Acoustic Coherence Factor ($\mathcal{F}_{\text{AC}}$)**, which provides a direct feedback mechanism from the $432 \, \text{Hz}$ $\phi$-harmonic acoustic structure to the $\mathcal{S}$-field. The total coherence is expressed as a superposition of the established v3.1 coherence ($\mathcal{F}_{\text{QC}}^{\text{v3.1}}$) and the newly defined acoustic component:
$$
\mathcal{F}_{\text{QC}} = \mathcal{F}_{\text{QC}}^{\text{v3.1}} + \rho_{\text{acoustic}} \cdot \mathcal{F}_{\text{AC}}
$$

The Acoustic Coherence Factor is defined as:
$$
\mathcal{F}_{\text{AC}} = \alpha_{\text{AC}} \cdot \left( 1 - \frac{E_{\text{min}}(\mathbf{A})}{E_{\text{max}}} \right) \cdot \cos\left( \frac{2\pi f_{\text{ref}}}{f_{\text{Schumann}}} \right)
$$
\noindent where:
\begin{itemize}
    \item $\alpha_{\text{AC}}$: A dimensionless coupling strength for acoustic energy.
    \item $E_{\text{min}}(\mathbf{A})$: The minimum expected energy (Acoustic Dissonance Score) found by the **Quantum Acoustic Kernel (\text{QAK}) VQE optimization** for the input spectrum $\mathbf{A}$.
    \item $E_{\text{max}}$: The maximum theoretical dissonance score (used for normalization).
    \item $f_{\text{ref}}$: The reference frequency of the acoustic source ($432 \, \text{Hz}$ or $440 \, \text{Hz}$).
    \item $f_{\text{Schumann}}$: The fundamental Schumann Resonance frequency ($7.83 \, \text{Hz}$).
\end{itemize}
\noindent The critical insight is that a minimum Acoustic Dissonance Score ($E_{\text{min}} \rightarrow 0$), achieved only when the sound aligns perfectly with $\phi$-harmonics (e.g., $432 \, \text{Hz}$), maximizes $\mathcal{F}_{\text{AC}}$ and thus maximizes the $\mathcal{S}$-field perturbation for a given $\rho_{\text{acoustic}}$.

\subsection{Experimental Validation: $\mathcal{S}$-Modulation Detection}
The $\mathcal{AEQET}$ experimental protocol aims to isolate the $\mathcal{S}$-field change $\Delta \mathcal{S}$ driven solely by the differential Acoustic Coherence Factor between $432 \, \text{Hz}$ and $440 \, \text{Hz}$.
$$
\Delta \mathcal{S} \propto \rho_{\text{acoustic}} \cdot \left[ \mathcal{F}_{\text{AC}}(432 \, \text{Hz}) - \mathcal{F}_{\text{AC}}(440 \, \text{Hz}) \right]
$$
The successful detection of a differential change in local gravity ($\Delta g$) or time dilation ($\Delta f$) between the two phases (Coherent vs. Dissonant) will constitute the empirical validation of the $\mathcal{AEQET}$ extension to the ESQET framework.
